Caustic: A Transactional Programming Language

### 2018-04-07 caustic-assets/paper/main.tex
Updated Library Type System

\subsubsection{Math}
The runtime natively supports just nine mathematical operations: $add$, $sub$, $mul$, $div$,
$pow$, $log$, $floor$, $sin$, and $cos$. However, these primitive operations are sufficient to
derive the entire Scala \href{https://www.scala-lang.org/api/2.12.1/scala/math/index.html}{math}
library using various mathematical identities and Taylor series approximations. The $div$,
$log$, $sin$, and $cos$ functions can actually be implemented in terms of the other primitive
operations; however, native support for them was included in the runtime to improve performance.
The standard library provides implementations for the functions enumerated in Table
\ref{table:math}.

>>>>

\subsubsection{Math}
The runtime natively supports just nine mathematical operations: $add$, $sub$, $mul$, $div$, $pow$,
$log$, $floor$,$sin$, and $cos$. However, these primitive operations are sufficient to derive the
entire Scala \href{https://www.scala-lang.org/api/2.12.1/scala/math/index.html}{math} library using
various mathematical identities and Taylor series approximations. The $div$, $log$, $sin$, and $cos$
functions can actually be implemented in terms of the other primitive operations; however, native
support for them was included in the runtime to improve performance. The standard library provides
implementations for the functions enumerated in Table \ref{table:math}.
